
# Load Libraries

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(tidyverse)
library(corrplot)
library(caret)
library(scales)
library(gridExtra)
library(maptools)
library(raster)
library(rgdal)
library(ggmap)
library(forcats)
library(reshape2)
```

# Load Data

```{r}
dt1 <- read.csv("russia_losses_equipment_correction.csv")
dt2 <- read.csv("russia_losses_equipment.csv")
dt3 <- read.csv("russia_losses_personnel.csv")
```

# Data Cleaning

- check for NA

- replace missing values

- Change the format of date in dt2, dt3

- Merge both datasets by date

- remove personnel. column 

- column 'vehicles and fuel tanks' that can be merged with columns fuel.tank and military.auto

- helicopter and aircraft can be merged into 'air_vehicles'


```{r}
any(is.na(dt1))
any(is.na(dt2))
any(is.na(dt3))
skimr::skim(dt1)
skimr::skim(dt2)
```

```{r}
#Change date datatype
dt2$date <- as.Date(dt2$date, "%Y-%m-%d")
dt3$date <- as.Date(dt3$date, "%Y-%m-%d")

#Merge by inner join
dt <- merge(dt2, dt3, by = "date", all = TRUE)

#Combine columns

for (i in 1:nrow(dt))
  {
    if (is.na(dt$vehicles.and.fuel.tanks[i])==FALSE) next
      else {
         dt$vehicles.and.fuel.tanks[i] = dt$military.auto[i] + dt$fuel.tank[i]
          }
  }

for (i in 1:nrow(dt)) 
  {
   dt$air_vehicles[i] = dt$aircraft[i] + dt$helicopter[i]
  }

#Remove columns that are not useful
dt <- subset(dt, select= -c (personnel., military.auto, fuel.tank, helicopter,aircraft))

#Set NA to 0 in mobile SRBM system
dt$mobile.SRBM.system[is.na(dt$mobile.SRBM.system)] <- 0 

#Replace NA with maxmimum in POW
dt$POW[is.na(dt$POW)] <- 496

# Replace any other NA present with 0
dt[is.na(dt)] <- 0
```

The column greatest.losses.direction contains Ukrainian cities that were hit. Here's what I'll do:

- Separate city names
- Generate latitude and longitude

```{r}
city <- unlist(strsplit(dt$greatest.losses.direction, ","))
city<- gsub(" ", "", city)
city<- unlist(strsplit(city, "and"))
location <- as.data.frame(table(city))
location$country <- "Ukraine"
class(location$city)
location$city <- as.character(location$city)
```


```{r}
#generating latitude and longitude
latlong <- geocode(location$city)
location <- cbind(location, latlong) %>% rename(long = lon)
write.csv(location, "location_Ukraine.csv", row.names = FALSE)
```

```{r}
head(location, 10)
```

```{r}
map_ukr <- get_map(location = c(31.1656, 48.3794), source = "google",zoom =6, maptype = "terrain")

ggmap(map_ukr)+
  geom_polygon(data= location, aes(x=long, y = lat, group = `city`), 
               fill='white', color='green', alpha = 0.4) +
  geom_point(data = location, aes(x = long, y = lat), color = 'red')
```

# Visualizations

1. Hit cities 

2. Loss of air weapons 

3. Loss of water weapons

4. Loss of field weapons

5. Loss of military: death + prisoners

```{r}
#Hit cities
Ukraine<-getData("GADM", country="UA", level=0)
Ukraine1<-getData("GADM", country="UA", level=1)

ggplot(location, aes(Freq, reorder(city, Freq), alpha=0.1))+
  geom_col(size=1, col="red")+
    labs(title="Number of Times Attacked", x="", y="")+
    theme(axis.text.x = element_text(size=10),
          axis.text.y = element_text(size=10),
          title= element_text(size=14, face="bold"),
           legend.position = "none")+
    scale_x_continuous(breaks = seq(0, max(dt$special.equipment), by=10))
```

```{r}
plot <- ggplot()+
    geom_polygon(data=Ukraine1, aes(long, lat, group=group), color="white",fill="dodgerblue1", alpha=0.8)+
    geom_point(data=location, aes(long,lat), color="red", size=6)+
    geom_text(data=location, aes(label=city, x= long, y=lat), size=6, color="black", fontface="bold", check_overlap=TRUE)+
    labs(title="Ukraine : Cities Hit by Russia", x="", y="")+
    theme(axis.text.x = element_text(size=6),
          axis.text.y = element_text(size=6),
          title= element_text(size=20, face="bold"))

plot
```

## Loss of Equipment

### Air-based Eqipment Loss

```{r}
#Air 
melt_air <- dt %>% dplyr::select(c("air_vehicles", "drone", "date"))
melt_air <- melt(melt_air, id = "date")

ggplot(melt_air, aes(x = date, y = value, color = variable)) +  
  geom_line(size=1.2)+
  scale_x_date(breaks='1 month', labels= date_format("%b"))+
  geom_text(data = subset(melt_air, date==c(min(dt$date),max(dt$date))), aes(label=value),hjust=1,vjust=0, size=4.5)+
  labs(title="Air-based Weapons Loss", x="Month", y = "Count", color=NULL)+
  theme(title= element_text(face="bold", hjust=4, size=20), 
        axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        legend.position = "top",
        panel.grid=element_line(size=0.4, color="gray", linetype=2))+
  scale_color_manual(values = c("orange3", "orange4"),
                     labels= c("Aircraft & Helicopter", "Drones"))
```

### Water-based Eqipment Loss

```{r}
# Water
melt_water <- dt %>% dplyr::select(c("naval.ship", "cruise.missiles", "date"))
melt_water <- melt(melt_water, id="date")

ggplot(melt_water, aes(x=date,y=value, color=variable))+
  geom_line(size=1.2)+
  scale_y_continuous( limits = c(0, 450), breaks= seq(0,450,by=50))+
  geom_text(data = subset(melt_water, date==max(dt$date)),
            aes(label=value,hjust=1,vjust=-1), 
            size=4.5)+
  labs(title="Water-based Weapons Loss", x="Month", y = "Count", color=NULL)+
  theme(title= element_text(face="bold", hjust=4, size=20), 
        axis.text.x = element_text(size=11),
        axis.text.y = element_text(size=11),
        legend.position = "top",
        panel.grid=element_line(size=0.4, color="gray", linetype=2))+
  scale_color_manual(values = c("dodgerblue1", "dodgerblue4"),
                     labels= c("Naval Ship", "Cruise Missiles"))
```

### Field-based Eqipment Loss

```{r}
# Field
library(viridis)
melt_field<- dt %>% dplyr::select(c("tank", "APC", "field.artillery","MRL","anti.aircraft.warfare","vehicles.and.fuel.tanks","date"))
melt_field <- melt(melt_field, id="date")

ggplot(melt_field, aes(x=date,y=value, color=variable))+
  geom_line(size=1.2)+
  geom_text(data = subset(melt_field, date==max(dt$date)),
            aes(label=value,hjust=1,vjust=-0.5), 
            size=3.5)+
  labs(title="Field-based Weapons Loss", x="Month", y = "Count", color=NULL)+
  scale_y_continuous( limits = c(0, 6000), breaks= seq(0,6000,by=1000))+
  theme(title= element_text(face="bold", hjust=0.5, size=20), 
        axis.text.x = element_text(size=11),
        axis.text.y = element_text(size=11),
        legend.position = "top",
        panel.grid=element_line(size=0.4, color="gray", linetype=2))+
        scale_color_brewer(type= "qual", palette = "Dark2")
```

### Special Eqipment Loss

```{r}
ggplot(dt, aes(x= date,y= special.equipment)) +
geom_line(size=1.8, color="red", alpha=0.5)+
labs(title="Special Equipment Loss",x="",y="",color=NULL)+
geom_text(aes(x=max(`date`), y=max(`special.equipment`), label = max(`special.equipment`)), size=4, vjust=-1)+
theme(title= element_text(face="bold", hjust=0.5, size=16),
        axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        legend.position = "bottom",
        legend.text = element_text(size=18),
        panel.grid=element_line(size=0.4, color="gray", linetype=2))+
        scale_color_brewer(type= "qual", palette = "Dark2")+
scale_x_date(date_breaks= "1 month", date_label = "%b")
```

## Loss of Military Personnels

### Death Toll

```{r}
#Dead Russian Military Personnel
dt %>% 
  group_by(month = lubridate::floor_date(date, "month")) %>%
  summarise(total=max(personnel)) %>%
  ggplot(., aes(x=month, y=total))+
  geom_col(aes(color=total, alpha=0.2))+
  labs(title="Dead Russian Military Personnel", x="", y="")+
  geom_text(aes(y=total,label=total), vjust=-0.8)+
   scale_color_steps(low = "orange", high = "red3")+
  theme(panel.grid = element_line(size=0.2, color="gray", linetype=2),
        axis.text.x = element_text(size=10),
        axis.text.y = element_text(size=10),
        title = element_text(size=20, face="bold"),
        legend.position = "none")+
  scale_x_date(breaks = "1 month", 
               label = date_format("%b"))
```

### Prisoners of War

Note: Data was unavailable since May. 

```{r}
#prisoners of war
dt %>% 
  group_by(month = lubridate::floor_date(date, "month")) %>%
  summarise(total=max(POW)) %>%
  ggplot(., aes(x=month, y=total))+
  geom_col(fill="black", alpha=0.4)+
  geom_line(color="red", size=1, linetype=1) + 
  geom_text(aes(y=total,label=total), vjust=-0.8)+
  scale_x_date(date_breaks = '1 month', date_labels = "%b")+
  scale_y_continuous(limits = c(0, 800), breaks= seq(0,800,by=100))
```

# Conclusion
 - Russia has been losing equipments of all forms - air, water, field, and special at an increasing rate every month.
 
- More and more Russian military personnels are dying in Ukraine.

- Those few military personnels alive, are being held as Prisoners of War in Ukraine.
